Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-20 krs-survey.tex
Added 'interaction' as subsection of knowledge acquisition
Added section on GSM

\paragraph{Perception}
\paragraph{Interaction}
\paragraph{External sources (Web, upper ontologies, ...)}
\paragraph{Learning}

@@

@@

@@

\begin{tabular}{lp{4cm}}
\toprule
{\bf Project} & {\bf Common-sense \par knowledge source} \\
\midrule
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\
OMRKF & {\it A priori} knowledge structure and axioms, custom set of instances\\
GSM &  \\
NKLR &  None \\
CAST Proxies &  None \\
Wrighteagle & \\
Vincze & \\
ARMAR &  \\
Hertzberg & \\
(DFKI Bremen) & \\
(JSK) & \\

@@

\multirow{5}{0.7cm}[-0.2cm]{\turn[1.5cm]{90}{\bf Expressive power}} & Logical formalism & Prolog & OWL-DL & {\sc CycL} &  &  &  & & Horn clauses \\
 & Expressive power & & & & & & & &  \\
 & OWA/CWA & CWA & OWA & & & & & & \\
 & Modeling uncertainty & +++ (extension) & & & & & & & + (\emph{candidate} entities) \\
 & Meta-cognition & ++ & ++ & & & & & & \\
\hline
\multirow{6}{0.2cm}{\turn{90}{\bf Model}} & Representation of space & & & & & & & & ++  \\
 & Representation of temporality & & & & & & & & +  \\
 & Context & & & & & & & & ++  \\
 & Alternative worlds & & +++ & & & & & &  \\
 & Introspection & + (SRDF) & & & & & & &  \\
 & Memory & & + & & & & & &  \\
\hline
\multirow{10}{0.2cm}{\turn{90}{\bf Reasoning}} & Standard FOL reasoning & +++ & +++ & & & & & & +  \\
 & Knowledge structure alteration & & ++ & & & & & &  \\
 & Lazy evaluation & +++ & & & & & & &  \\
 & Reasoning under uncertainty & ++ (extension) & & & & & & & \\
 & Non-monotonic reasoning & & & & & & & &  \\
 & Presupposition accomodation & & & & & & & +++ & \\
 & Prediction, projection, diagnosis & & & & & & & & \\
 & Physics-based reasoning & +++ (extension) & & & & & & &  \\
 & Planning & + & +++ (external module) & & & & & & + \\
 & Learning & & & & & & & &  \\
\hline
\multirow{3}{0.7cm}{\turn[1cm]{90}{\bf Knw. acq.}} & Acquisition techniques & & & & & & & & \\
 & Grounding & & & & & & & & ++ \\
 & Instanciation & & & & & & & & \\
\hline
\multirow{4}{0.2cm}{\turn{90}{\bf Integ.}} & ...with sensori-motor layers & & & & & & & & ++ \\
 & ...with executive layers & & & & & & & & ++ \\
 & Monitoring and debugging & & & & & & & & \\
 & Performances & & & & & & & & \\

>>>>

@@

\subsubsection{Interaction with other agents}
\label{sect|interactions}

@@

\subsection{GSM}
\label{sect|gsm}

GSM (for \emph{Grounded Situation Model})~\cite{Mavridis2006} is a knowledge
representation system primarly built to ``facilitate cross-modal
interoperability'',  especially in the context of verbal interaction with a
robot.

Unlike most of the previously presented systems, GSM does not rely on any
formal language but rather on a layered datastructure (Figure~\ref{fig|gsm})
that organizes the surrounding world into agents and relations between agents.
Each agent (any animate or inanimate object) is attached to a physical model (made
of \emph{body parts} that have properties like their position, color, etc.) and
a mental model (which is a recursively embedded GSM, thus allowing a sort of
theory of mind).

\begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{gsm.pdf}

    \caption{Simplified hierachical structure of the Grounded Situation Model,
    based on~\cite{Mavridis2006}}

    \label{fig|gsm}
   \end{figure}

Properties are represented in three layers: a stochastic representation, close
to sensory percepts, a \emph{continous single-valued} encoding of the
stochastic model, and a discrete, categorical model.

One notable feature of GSM is the \emph{bidirectionality} of the grounding
process: not only sensor percepts are abstracted into categories suitable for
human conversation, but human utterance (like ``There is a red ball in the
center of the table'') can also be turned into property descriptions. This
basically enable the knowledge representation system of the robot to
\emph{imagine} entities.

GSM also features several strategies for managing time and events.
\emph{Moments} are created by storing timestamped snap-shots of GSM, and
\emph{event classifiers} allow to define and detect events.

\paragraph{Experiments} GSM has mostly been tested on table-top manipulation
and interaction tasks (a ``conversational helping hand'' as stated by the
authors) realized on a 7-DOF arm equipped with force feedback, cameras for blob
tracking and speech recognition (Sphinx4).

@@

\begin{tabular}{lp{4cm}}
\toprule
{\bf Project} & {\bf Common-sense \par knowledge source} \\
\midrule
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\
NKLR &  None \\
CAST Proxies &  None \\
GSM &  Predefined categories \\
OMRKF & {\it A priori} knowledge structure and axioms, custom set of instances\\
Wrighteagle & \\
Vincze & \\
ARMAR &  \\
Hertzberg & \\
(DFKI Bremen) & \\
(JSK) & \\

@@

\multirow{5}{0.7cm}[-0.2cm]{\turn[1.5cm]{90}{\bf Expressive power}} & Logical formalism & Prolog & OWL-DL & {\sc CycL} &  &  &  & & Horn clauses \\
 & Expressive power & & & & & & & &  \\
 & OWA/CWA & CWA & OWA & & & & & & \\
 & Modeling uncertainty & +++ (extension) & & & & & & ++ (stochastic) & + (\emph{candidate} entities) \\
 & Meta-cognition & ++ & ++ & & & & & & \\
\hline
\multirow{6}{0.2cm}{\turn{90}{\bf Model}} & Representation of space & & & & & & & & ++  \\
 & Representation of temporality & & & & & & & + (snapshots) & +  \\
 & Context & & & & & & & & ++  \\
 & Alternative worlds & & +++ & & & & ++ & &  \\
 & Introspection & + (SRDF) & & & & & & &  \\
 & Memory models & & + & & & & & &  \\
\hline
\multirow{10}{0.2cm}{\turn{90}{\bf Reasoning}} & Standard FOL reasoning & +++ & +++ & & & & & & +  \\
 & Knowledge structure alteration & & ++ & & & & & &  \\
 & Lazy evaluation & +++ & & & & & & &  \\
 & Reasoning under uncertainty & ++ (extension) & & & & & + & & \\
 & Non-monotonic reasoning & & & & & & & &  \\
 & Presupposition accomodation & & & & & & & +++ & \\
 & Prediction, projection, diagnosis & & & & & & & & \\
 & Physics-based reasoning & +++ (extension) & & & & & & &  \\
 & Planning & + & +++ (external) & & & & & & + \\
 & Learning & & & & & & & &  \\
\hline
\multirow{3}{0.7cm}{\turn[1cm]{90}{\bf Knw. acq.}} & Acquisition techniques & & & & & & & & \\
 & Grounding & & & & & & & ++ & ++ \\
 & Interaction & & +++ (external) & & & & & +++ & \\
 & Instanciation & & & & & & & & \\
\hline
\multirow{4}{0.2cm}{\turn{90}{\bf Integ.}} & ...with sensori-motor layers & & & & & & & + & + \\
 & ...with executive layers & & & & & & & + & ++ \\
 & Monitoring and debugging & & & & & & & & \\
 & Performances & & & & & & & & \\
